Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-05-07 paper/pedestrian_forecasting_iros_2017.tex
All citations should be resolved for now.

\rtext{On the other hand, many authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians. Early work by [helbig] and [Xu] describe pedestrians interactions using physically motivated methods. Several models [yamaguchi, yi, pellegrini you’ll never] derive their motion models from [helbing] who incorporate collision avoidance through an interaction potential which repels pedestrians from each other, leading to forms of what is called Linear Trajectory Avoidance (LTA). However LTA suffers from not planning for other pedestrian’s positions at future times. [emonet], [hospedales], and [wang: unsupervised] all take optical flow as input. [wang] and [emonet] both use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), where [hospedales] substitutes a Markov model. These models are not agent based, and the lack of an explicit motion model limits their predictive power in situations where we know more about the data. [koppula and saxena] predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances for humans and objects based on observed objectives within the scene. [Tay], [Wang jw], and [Trautman] create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories. [alahi] uses Long Short-Term Memory to learn pedestrian motion models without making implicit (as in the case of CRFs) or explicit (in the case of social forces) assumptions about the manner in which agents will interact. [alahi] outperformed LTA, the social forcing based on [yamaguchi],  and IGP from [trautman]. Along with its quick run time, this establishes [alahi] as state-of-the-art for socially based models, and so we our algorithm to theirs. }

@@

  \subsection{Learning the Vector Fields}
 We begin by identifying the number of possible vector-fields.
  To do this we use a clustering algorithm on the trajectories observed in a scene to categorize them into groups.
  %In principal, any clustering algorithm could accomplish this.
\rtext{We then cluster in $\mathbb{R}^4$ using Affinity Propagation[17] and a custom distance measure defined by $d((x_1, x_2, x_3, x_4),\mathbf{y}) : \mathbb{R}^4 \times \mathbb{R}^4 \to \mathbb{R} = \min \left\{ d_e((x_1, x_2, x_3, x_4), \mathbf{y}), d_e((x_3, x_4, x_1, x_2), \mathbf{y}) \right\}$, for the euclidean distance $d_e$. This function measures the distance between the endpoints irrespective of their ordering. The scale of the datasets we tested on had large enough spatial scale that clustering based on endpoints captured people moving from destination to destination, e.g. from a storefront to the sidewalk at the edge of a scene. On our data, other distance measures from \todo{[Morris and Trivedi]} and \todo{[Lee 2007]} didn't identify coherent motion models. This is partly due to the fact that oftentimes pedestrians would take slightly different routes to get to their destination, and the cumulative effect on the distance measures is enough to hinder the clustering.We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}
  This clustering of the end-points induces a clustering of the trajectories.
  Suppose we obtain clusters $S_1, \dots, S_n$ consisting of trajectories from our data set, as well as a set of unclassified trajectories, $S_0$.

@@

This section establishes our methods performance and compares it to the model from \cite{Kitani2012} and a random walk.
We implement our model as well as our evaluation code in Python 2.6. 
Our implementation is available online\footnote{https://github.com/OkayHughes/iros2017\_pedestrian\_forecasting}.
\rtext{We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}
\rtext{Our analysis was conducted on the Coupa, Bookstore, Death Circle, and Gates scenes from the dataset from [13], with a total of 142 trajectories analyzed.}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/the_results.eps}
	\caption{\rtext{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the model from [asdfasdf] 100 times in order to give them the best chance in this analysis, but their confidence combined with the over-reliance on social forces at moderate-to-large lowered their performance.}}
	\label{fig:auc_vs_time}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/MHD_results.eps}
	\caption{\rtext{A comparison of the Modified Hausdorff Distance from the ground truth of the pedestrian to a 1000 point sample from each distribution. The method from [asdfasdf] does very well at short time scales due to its confidence, but we outperform all other methods at intermediate times. At long timescales the MHD to the trajectory of most algorithms converges. Our method increases positional uncertainty with time, and so \cite{Kitani2012} outperforms us because they know the end point and we do not, and [asdfasdf] places too much significance on the initial positions of other pedestrians at large time scales.}}
	\label{fig:mhd_vs_time}
\end{figure}

>>>>

\rtext{On the other hand, many authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians. Early work by \cite{Helbing1995} and \cite{Xu2012} describe pedestrians interactions using physically motivated methods. Several models such as \cite{Yamaguchi2011}, \cite{Yi2016}, and \cite{Pellegrini2009} derive their motion models from \cite{Helbing1995} who incorporate collision avoidance through an interaction potential which repels pedestrians from each other, leading to forms of what is called Linear Trajectory Avoidance (LTA). However LTA suffers from not planning for other pedestrian’s positions at future times. \cite{Emonet2011}, \cite{Hospedales2009} , and \cite{Wang2009}  all take optical flow as input. \cite{Wang2009} and \cite{Emonet2011} both use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), where \cite{Hospedales2009} substitutes a Markov model. These models are not agent based, and the lack of an explicit motion model limits their predictive power in situations where we know more about the data. \cite{Koppula2016} predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances for humans and objects based on observed objectives within the scene. \cite{Tay2008} , \cite{Wang2008}, and \cite{Trautman2015} create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories. \cite{Alahi2016} uses Long Short-Term Memory to learn pedestrian motion models without making implicit (as in the case of CRFs) or explicit (in the case of social forces) assumptions about the manner in which agents will interact. \cite{Alahi2016} outperforms LTA, social forcing based on \cite{Yamaguchi2011},  and IGP from \cite{Trautman2015}. Along with its quick run time, this establishes \cite{Alahi2016} as state-of-the-art for socially based models, and so we our algorithm to theirs.}

@@

  \subsection{Learning the Vector Fields}
 We begin by identifying the number of possible vector-fields.
  To do this we use a clustering algorithm on the trajectories observed in a scene to categorize them into groups.
  %In principal, any clustering algorithm could accomplish this.
\rtext{We then cluster in $\mathbb{R}^4$ using Affinity Propagation \cite{FreyDueck2007} and a custom distance measure defined by $d((x_1, x_2, x_3, x_4),\mathbf{y}) : \mathbb{R}^4 \times \mathbb{R}^4 \to \mathbb{R} = \min \left\{ d_e((x_1, x_2, x_3, x_4), \mathbf{y}), d_e((x_3, x_4, x_1, x_2), \mathbf{y}) \right\}$, for the euclidean distance $d_e$. This function measures the distance between the endpoints irrespective of their ordering. The scale of the datasets we tested on had large enough spatial scale that clustering based on endpoints captured people moving from destination to destination, e.g. from a storefront to the sidewalk at the edge of a scene. On our data, other distance measures from \cite{Morris2009} and \cite{Lee2007} didn't identify coherent motion models. This is partly due to the fact that oftentimes pedestrians would take slightly different routes to get to their destination, and the cumulative effect on the distance measures is enough to hinder the clustering. We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}
  This clustering of the end-points induces a clustering of the trajectories.
  Suppose we obtain clusters $S_1, \dots, S_n$ consisting of trajectories from our data set, as well as a set of unclassified trajectories, $S_0$.

@@

This section establishes our methods performance and compares it to the model from \cite{Kitani2012} and a random walk.
We implement our model as well as our evaluation code in Python 2.6. 
Our implementation is available online\footnote{https://github.com/OkayHughes/iros2017\_pedestrian\_forecasting}.
\rtext{We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}
\rtext{Our analysis was conducted on the Coupa, Bookstore, Death Circle, and Gates scenes from the dataset from \cite{Robicquet2016}, with a total of 142 trajectories analyzed.}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/the_results.eps}
	\caption{\rtext{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model 100 times in order to give them the best chance in this analysis, but their confidence combined with the over-reliance on social forces at moderate-to-large timescales lowered their performance.Though including social forces into the model is out of the scope of this paper, its incorporation could begin as follows.  In the current motion model with a single vector field, the acceleration of the $i$th agent is given by $\ddot{x}_i = s^2 DX(x_i) \cdot X(x_i)$.  Incorporating a social force $F_{i}$ acting on the $i$th agent can be done by instead asserting $\ddot{x}_i = s^2 DX(x) \cdot X(x) + F_i$.  Usually $F_{i} = \sum_{j} \nabla U( x_j - x_i)$ where $U$ is an interaction potential \cite{Helbing1995} .}}
	\label{fig:auc_vs_time}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/MHD_results.eps}
	\caption{\rtext{A comparison of the Modified Hausdorff Distance from the ground truth of the pedestrian to a 1000 point sample from each distribution. The method from \cite{Alahi2016} does very well at short time scales due to its confidence, but we outperform all other methods at intermediate times. At long timescales the MHD to the trajectory of most algorithms converges. Our method increases positional uncertainty with time, and so \cite{Kitani2012} outperforms us because they know the end point and we do not, and \cite{Alahi2016} places too much significance on the initial positions of other pedestrians at large time scales.}}
	\label{fig:mhd_vs_time}
\end{figure}
